---
title: "Baseline_dataAnalysis"
author: "Bernice Cheung"
date: "4/6/2021"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, echo=FALSE,warning=FALSE,message=FALSE}
library(tidyverse)
library(psych)
library(ggplot2)
library(stringr)
library(knitr)
library(lme4)
library(nFactors)
library(corrplot)
library(janitor)
library(kableExtra)
library(GPArotation)
library(here)
```

load data: 246 subjects, with 845 goals are included in the following analysis

```{r}
goalRating_long_R <- read.csv(here("Baseline", "Inputs", "goalRating_long_R.csv"),stringsAsFactors = F)

wideDf <- read.csv(here("Baseline", "Inputs", "wideDf.csv"),stringsAsFactors = F)

indivDiffDf <- read.csv(here("Baseline", "Inputs", "indivDiffDf.csv"),stringsAsFactors = F)

goalListDf <- read.csv(here("Baseline", "Outputs", "listedGoals.csv"), stringsAsFactors = F)
```

# Data Screening for goal representation assessment

### Missing data

Check the number of missing data per variable, and below is the top 5 variables. Missing data is rare for all variables
```{r}
# check the number of "I'm not sure" responses per variable
totalGoal <- nrow(goalRating_long_R)/41

goalRating_long_R %>%
  filter(is.na(rating)) %>%
  tabyl(variable) %>%
  mutate(percent = n/totalGoal) %>%
  arrange(desc(percent)) %>%
  head(5)
```

### The "I'm not sure" response

"construal_level","approach_avoidance" and "attainment_maintenance" question have an option for "I'm not sure" because they ask subjects to categorize their goals.  

around 1% of the goals had "I'm not sure" as the response. 
```{r}
# check the number of "I'm not sure" responses per varialbe
goalRating_long_R %>%
  filter(rating == 99) %>%
  tabyl(variable) %>%
  mutate(percent = n/totalGoal) %>%
  arrange(desc(percent))
```

### The "not specified" response  

temporal_duration, frequency and end_state_specificity question have an option for "not specified" because they ask about features that may not be applicable to all goals.  

around 5% of the responses are "not specified"
```{r}
# check the number of "not specified" responses per varialbe
goalRating_long_R %>%
  filter(rating == 999) %>%
  tabyl(variable) %>%
  mutate(percent = n/totalGoal) %>%
  arrange(desc(percent))
```

### Transform all special cases to NAs

All "I'm not sure" and "not specified" responses will be treated as missing data. 

```{r}
# transform 99 & 999 to NAs
goalRating_long_R <- goalRating_long_R %>% 
  mutate(rating = replace(rating, rating == 99 | rating == 999, NA))
```


### The number of claimed goals

Descriptive on the number of goals subject claimed to have prior to listing them (lower than the previous mTurk study)
```{r}
describe(wideDf$total_goal)
```

Visualize the number of claimed goals per subject after excluding the extreme value (> 20) (1 claimed 40)
```{r}
breaks = (1:20)
wideDf %>% 
  filter(total_goal < 20) %>%
  ggplot(aes(x = total_goal)) + 
  scale_x_continuous(labels=scales::comma(breaks, accuracy = 1), breaks=breaks) + 
  geom_histogram(fill = "orange", 
                 colour = "black",
                 binwidth = 1) + 
  labs(x="Number of claimed goals", y="# of participants") +
  theme_classic(base_size = 18) 
```


The percentage of subjects who claimed having more than 5 goals: 9.8% 
```{r}
# get the number of total subject
totalSub <- nrow(indivDiffDf)

length(wideDf$total_goal[wideDf$total_goal>5])/totalSub
```

Descriptive on the number of goals participants actual listed (similar to all previous study)
```{r}
describe(wideDf$listNum)
```

```{r}
breaks <- (1:5)
wideDf %>% 
  ggplot(aes(x = listNum)) + 
  scale_x_continuous(labels=scales::comma(breaks, accuracy = 1), breaks=seq(1, 5, by = 1)) + 
  geom_histogram(fill = "orange", 
                 colour = "black",
                 binwidth = 1) + 
  labs(x="Number of listed goals", y="# of participants") +
  theme_classic(base_size = 18) 
```

number of people who listed 1 goal: 9
```{r}
length(wideDf$listNum[wideDf$listNum == 1])
```


descriptive on the differences between the number of claimed goals and listed goals (after exclude the extreme case)
```{r}
wideDf <-wideDf %>%
  mutate(diffNum = total_goal - listNum)

goalDf_sum_wide_clean <- wideDf %>%filter(total_goal < 20)
  
describe(goalDf_sum_wide_clean$diffNum)

breaks <- (-4:15)
goalDf_sum_wide_clean %>% 
  ggplot(aes(x = diffNum)) + 
  scale_x_continuous(labels=scales::comma(breaks, accuracy = 1), breaks=breaks) + 
  geom_histogram(fill = "orange", 
                 colour = "black",
                 binwidth = 1) + 
  labs(x="Number of claimed goals - listed goals", y="# of participants") +
  theme_classic(base_size = 18) 
```


percentage of people who listed more goals than they claimed: 13%
```{r}
length(wideDf$diffNum[wideDf$diffNum <0])/totalSub *100
```


percentage of people who listed less goals more than they claimed: 14%
```{r}
length(wideDf$diffNum[wideDf$diffNum >0])/totalSub *100
```


# Goal Representation Ratings

### Descriptive stats
```{r}
# descriptive stats for each variable 
goalRating_long_R %>%
  dplyr::select(variable, rating) %>%
  group_by(variable) %>%
  summarize(mean = mean(rating, na.rm = TRUE),
            sd = sd(rating, na.rm = TRUE), 
            n = n(),
            min = min(rating, na.rm = TRUE),
            max = max(rating, na.rm = TRUE),
            skew = skew(rating, na.rm = T), 
            kurtosi = kurtosi(rating, na.rm = T)
            ) %>%
  arrange(skew) %>%
  kable(format = "html", escape = F) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F,position = "center")
```


The trend looks more skewed than previous MTurk data
```{r fig.width = 10, fig.height=10, warning=FALSE}
# histograms for each dimension
goalRating_long_R %>%
  ggplot(aes(x = rating)) +
    geom_histogram(fill   = "orange",
                   colour = "black",
                   alpha  = .6) +
    facet_wrap(~variable, nrow = 7)
```

### correlational matrix across all variables

"pairwise.complete.obs" is used for generating correlation matrix.The correlations make sense
```{r fig.height=20, fig.width=20}
# transform the long format to short format
goalDf_wide <- goalRating_long_R %>% spread (variable, rating)

# generate a correctional matrix
corrM_all <- goalDf_wide %>% 
  dplyr :: select(affordance:visibility) %>% 
  cor(use = "pairwise.complete.obs")

# visualization
corrplot(corrM_all, method = "circle",number.cex = .7, order = "AOE", addCoef.col = "black",type = "upper",col= colorRampPalette(c("midnightblue","white", "orange"))(200))

# write the wide format
write.csv(goalDf_wide, here("Baseline", "Outputs", "goalDf_wide.csv"), row.names = F)

left_join(goalListDf, goalDf_wide, by = c("MTurkCode","goal_order" = "goal")) %>%
  write.csv(., here("Baseline", "Outputs", "goalList_rating.csv"),row.names = F)
```

### Variance Partition

Only the 31 variables for goal representation are included. Only around 6.6% of the variance is on the between subject level. 

```{r}
# subset the long format dataset for only the 31 goal representation variable
goal_striving <- c("commitment", "urgency", "effort", "initial_time_R", "regret", "procrastination", "failure", "self_resources", "other_resources", "implementation_intention")
goalDf_R_long <- goalRating_long_R[!goalRating_long_R$variable %in% goal_striving,]

# generate a multilevel model with subject as the random intercept
mlm <-lmer(rating ~ variable + (1|MTurkCode), data = goalDf_R_long)

# calculate the variance partition coefficient and transform to ICC
VarCorr(mlm) %>%
  as_tibble() %>%
  mutate(icc=vcov/sum(vcov)) %>%
  dplyr :: select(grp, icc)

Raw <- VarCorr(mlm) %>%
  as_tibble() %>%
  mutate(Raw=vcov/sum(vcov)) %>%
  dplyr :: select(Raw)
```


# Exploritory Factor Analysis

### Data transformation 

26 variables are included. Ordinal variables are not included: "temporal_duration" & "end_state_specificity" and "frequency"; appoach_avoidance_R & attainment_maintainance_R are also dropped because these 2 variables are more relevant to the phrasing/content of a goal than the perception of a goal. This step is consistent with the SONA study

```{r}
# Exclude the 8 variables related to goal striving progress
goalDf_R_wide <- goalDf_wide[,!names(goalDf_wide) %in% goal_striving]

# Exclude 5 goal representation variables and other columns with irrelevant data
goal_exclude <- c("temporal_duration", "end_state_specificity_R", "frequency_R", "attainment_maintenance_R", "approach_avoidance_R")
goalDf_EFA <- goalDf_R_wide[,!names(goalDf_R_wide) %in% goal_exclude]
goalDf_EFA <- subset(goalDf_EFA, select = affordance : visibility)

# Generate a correctional matrix 
corrM_raw <- cor(goalDf_EFA, use = "pairwise")

# export the correlation matrix
write.csv(corrM_raw,here("Baseline", "Outputs", "baseline_corrRating_raw.csv"))
write.csv(goalDf_EFA,here("Baseline", "Outputs", "baseline_EFA_raw.csv"), row.names = F)
```

### evaluate the number of factors
```{r}
# use Very Simple Structure criterion
res_vss <- psych :: nfactors(corrM_raw, n = 10, rotate = "promax", diagonal = FALSE, fm = "minres", 
n.obs=845,title="Very Simple Structure",use="pairwise",cor="cor")

# select useful parameters and organize them into a table
cbind(1:10, res_vss$map) %>%
  as_tibble() %>%
  rename(., factor = V1, map = V2) %>%
  cbind(., res_vss$vss.stats) %>%
  select(factor, map, fit, complex, eChisq, SRMR, eCRMS, eBIC, eRMS) %>%
  kable(format = "html", escape = F, caption = "VSS output -mTurk") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F,position = "center",fixed_thead = T)

```

```{r}
# Use the Scree plot to identify the number of factors have Eigenvalues >1 and the output from the Parallel analysis

ev <- eigen(corrM_raw)
ap <- parallel(subject=nrow(goalDf_EFA),var=ncol(goalDf_EFA),
  rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```


## Extract factors

```{r}
# extract 4 factors
fa_new_4 <-fa(r=corrM_raw, nfactors=4,n.obs = 845, rotate="promax", SMC=FALSE, fm="minres")
```

## Factor loadings
```{r}
fa.diagram(fa_new_4)
```

```{r}
# visualization
loadings <- fa.sort(fa_new_4)$loadings
loadings <- as.data.frame(unclass(loadings))
colnames(loadings) <- c("Value","External", "Clarity", "Consensus")
loadings$Items <- rownames(loadings)
loadings.m <- loadings %>% gather(-Items, key = "Factor", value = "Loading")
colOrder <- c("Value","External", "Clarity", "Consensus")
rowOrder <- rev(rownames(loadings))
loadings.m<- arrange(mutate(loadings.m,Items=factor(Items,leve=rowOrder)),Items)
loadings.m<- arrange(mutate(loadings.m,Factor=factor(Factor,leve=colOrder)),Factor)

ggplot(loadings.m, aes(Items, abs(Loading), fill=Loading)) + 
  facet_wrap(~ Factor, nrow=1) + #place the factors in separate facets
  geom_bar(stat="identity") + #make the bars
  coord_flip() + #flip the axes so the test names can be horizontal  
  #define the fill color gradient: blue=positive, red=negative
  scale_fill_gradient2(name = "Loading", 
                       high = "orange", mid = "white", low = "midnightblue", 
                       midpoint=0, guide="colourbar") +
  ylab("Loading Strength") + #improve y-axis label + 
  ggtitle("Four Factor Solution from mTurk Sample 2") +
  geom_hline(yintercept = 0.3, color = "red", linetype="dotted") +
  theme_bw(base_size=10)
```

interfactor correlation: 

The correlation between clarity and value seems weird
```{r}
fa_new_4$Phi %>% 
  as.tibble() %>% 
  dplyr::rename(External = MR1, Value = MR2, Clarity = MR3, Cansensus = MR4) %>%
  round(.,2) %>%
  remove_rownames() %>%
  mutate(factor = colnames(.)) %>%
  select(factor, everything()) %>%
  kable(format = "html", escape = F, caption = "<center>Factor Correlation of mTurk Sample 2</center>") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F,position = "center",fixed_thead = T)
```

## Model fit
```{r}
data.frame(sample = "mTurk", factors = 4, items = 26, observation = 845, chi = fa_new_4$chi, BIC = fa_new_4$BIC, fit = fa_new_4$fit, RMSEA = fa_new_4$RMSEA[1], cumVar = max(fa_new_4$Vaccounted[3,]), complexity = mean(fa_new_4$complexity)) %>%
  remove_rownames() %>%
  kable(format = "html", escape = F) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F,position = "center")

sona_factorFit <- data.frame(sample = "mTurk", factors = 4, items = 26, observation = 845, chi = fa_new_4$chi, BIC = fa_new_4$BIC, fit = fa_new_4$fit, RMSEA = fa_new_4$RMSEA[1], cumVar = max(fa_new_4$Vaccounted[3,]), complexity = mean(fa_new_4$complexity))

#write.csv(sona_factorFit, "./outputs/mTurk2_factorFit.csv", row.names = F)
```


## 6 factor model


```{r}
# extract 6 factors
fa_new_6 <-fa(r=corrM_raw, nfactors=6,n.obs = 845, rotate="promax", SMC=FALSE, fm="minres")
```

## Factor loadings
```{r}
fa.diagram(fa_new_6)
```
```{r}
# visualization
loadings <- fa.sort(fa_new_6)$loadings
loadings <- as.data.frame(unclass(loadings))
colnames(loadings) <- c("Value","External", "Attainability", "Instrumentality", "Consensus", "Measurability")
loadings$Items <- rownames(loadings)
loadings.m <- loadings %>% gather(-Items, key = "Factor", value = "Loading")
colOrder <- c("Value","External", "Attainability", "Instrumentality", "Consensus", "Measurability")
rowOrder <- rev(rownames(loadings))
loadings.m<- arrange(mutate(loadings.m,Items=factor(Items,leve=rowOrder)),Items)
loadings.m<- arrange(mutate(loadings.m,Factor=factor(Factor,leve=colOrder)),Factor)

ggplot(loadings.m, aes(Items, abs(Loading), fill=Loading)) + 
  facet_wrap(~ Factor, nrow=1) + #place the factors in separate facets
  geom_bar(stat="identity") + #make the bars
  coord_flip() + #flip the axes so the test names can be horizontal  
  #define the fill color gradient: blue=positive, red=negative
  scale_fill_gradient2(name = "Loading", 
                       high = "orange", mid = "white", low = "midnightblue", 
                       midpoint=0, guide="colourbar") +
  ylab("Loading Strength") + #improve y-axis label + 
  ggtitle("Four Factor Solution from mTurk Sample 2") +
  geom_hline(yintercept = 0.3, color = "red", linetype="dotted") +
  theme_bw(base_size=10)
```


